---
title: "Testing WORCS"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")

library(worcs)
library(here)
library(dplyr)
library(tidygraph)
library(ggraph)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/christine-hvw/worcs_test>.

# The Socium Coauthorship Network

The data contains information on co-authorship in the [Socium research center](https://www.socium.uni-bremen.de/) (University of Bremen) between 2010 and 2020.

```{r data}
net_soc <- readRDS(here("data-processed", "net_soc.rds"))
```

## Department Assortativity

Let's inspect with plot whether co-authorship tends to be more prevalent within than across departments:

```{r plot}
ggraph(net_soc, layout = "fr") +
  geom_edge_link() +
  geom_node_point(aes(fill = as.factor(dep_cat)), 
                  shape = 21, size = 2) +
  labs(fill = "Department", caption = "Co-authorship network of SOCIUM members.") +
  theme_graph(base_family="sans")
```

Apart from a visual inspection, we can also calcualte the assortativity coefficient^[I use the assortativity coefficient for discrete characteristics as proposed by @newman2003, which takes the value 0 when there is no assortative mixing and 1 when there is complete assortativity.]:

```{r assortativity}
assort_coef <- net_soc %>% 
  activate(nodes) %>% 
  mutate(assort = graph_assortativity(dep_cat, directed = FALSE)) %>% 
  pull(assort) %>% 
  unique()
```

The coefficient for department assortativity is **`r round(assort_coef, 3)`**, meaning: co-authorship is far more prevalent within than between departments.


